Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-07-03 paper.tex
add experiment info

>>>>

==Experiments Description==

Aim: To obtain a detailed understanding of data movements and metadata changes over a set of cloud instances for a given storage system working in conjunction with a workflow encoded application execution.

Statement: Run a workflow using Swift with S3, Mosa and FusionFS each over a set number of cloud instances for a set workflow I/O profile.

1. Workflow: Skeleton generated synthetic workflow (essentially a DAG). 5
stages, one branch. Each stage has between 10 and 100 tasks with a total of 500
computationally medium intensive tasks. Stages produce and consume data
arbitrarily. Approximately between 100 and 1000 MB of I/O per workflow run.

2. Swift: Run with SwiftK with explicit data movement over locally hosted data
and with SwiftT with implicit data movement over storage system hosted data.
Logging enabled.

3. S3: Run S3 in remote and mounted with fuse mode. Enable full Fuse logging.

4. Mosa and FusionFS: Run'em in full logging mode with default configuration.

5. Cloud instances: Run over 20 and 40 cloud instances (2 regions) of type
medium : 2 core 10G+ memory instances. Need to work out the cost.

Assuming a hypothetical commandline controlling experiment parameters, we will
have the following 8 sets of experiments with 5 runs in each resulting in a
grand total of 40 runs.

runexp swiftK --datasize=100m  --cloudinstances=20 --storagesystem=none #baseline distributed workflow execution, classic Swift, no storage system, job and data distribution is done by Swift.
runexp swiftK --datasize=200m  --cloudinstances=20 --storagesystem=none 
runexp swiftK --datasize=500m  --cloudinstances=20 --storagesystem=none
runexp swiftK --datasize=750m  --cloudinstances=20 --storagesystem=none
runexp swiftK --datasize=1000m --cloudinstances=20 --storagesystem=none

runexp swiftK --datasize=100m  --cloudinstances=40 --storagesystem=none #cloud instances across two regions with explicit staging
runexp swiftK --datasize=200m  --cloudinstances=40 --storagesystem=none
runexp swiftK --datasize=500m  --cloudinstances=40 --storagesystem=none
runexp swiftK --datasize=750m  --cloudinstances=40 --storagesystem=none
runexp swiftK --datasize=1000m --cloudinstances=40 --storagesystem=none

runexp swiftT --datasize=100m  --cloudinstances=20 --storagesystem=s3fs #S3 as mounted FS via FUSE, one region, implicit staging
runexp swiftT --datasize=200m  --cloudinstances=20 --storagesystem=s3fs
runexp swiftT --datasize=500m  --cloudinstances=20 --storagesystem=s3fs
runexp swiftT --datasize=750m  --cloudinstances=20 --storagesystem=s3fs
runexp swiftT --datasize=1000m --cloudinstances=20 --storagesystem=s3fs

runexp swiftT --datasize=100m  --cloudinstances=40 --storagesystem=s3fs #S3 as mounted FS via FUSE, two regions, implicit staging
runexp swiftT --datasize=200m  --cloudinstances=40 --storagesystem=s3fs
runexp swiftT --datasize=500m  --cloudinstances=40 --storagesystem=s3fs
runexp swiftT --datasize=750m  --cloudinstances=40 --storagesystem=s3fs
runexp swiftT --datasize=1000m --cloudinstances=40 --storagesystem=s3fs

runexp swiftT --datasize=100m  --cloudinstances=20 --storagesystem=mosa #same as above, except with mosa
runexp swiftT --datasize=200m  --cloudinstances=20 --storagesystem=mosa
runexp swiftT --datasize=500m  --cloudinstances=20 --storagesystem=mosa
runexp swiftT --datasize=750m  --cloudinstances=20 --storagesystem=mosa
runexp swiftT --datasize=1000m --cloudinstances=20 --storagesystem=mosa

runexp swiftT --datasize=100m  --cloudinstances=40 --storagesystem=mosa
runexp swiftT --datasize=200m  --cloudinstances=40 --storagesystem=mosa
runexp swiftT --datasize=500m  --cloudinstances=40 --storagesystem=mosa
runexp swiftT --datasize=750m  --cloudinstances=40 --storagesystem=mosa
runexp swiftT --datasize=1000m --cloudinstances=40 --storagesystem=mosa

runexp swiftT --datasize=100m  --cloudinstances=20 --storagesystem=fusion #same as above, except with fusion
runexp swiftT --datasize=200m  --cloudinstances=20 --storagesystem=fusion
runexp swiftT --datasize=500m  --cloudinstances=20 --storagesystem=fusion
runexp swiftT --datasize=750m  --cloudinstances=20 --storagesystem=fusion
runexp swiftT --datasize=1000m --cloudinstances=20 --storagesystem=fusion

runexp swiftT --datasize=100m  --cloudinstances=40 --storagesystem=fusion
runexp swiftT --datasize=200m  --cloudinstances=40 --storagesystem=fusion
runexp swiftT --datasize=500m  --cloudinstances=40 --storagesystem=fusion
runexp swiftT --datasize=750m  --cloudinstances=40 --storagesystem=fusion
runexp swiftT --datasize=1000m --cloudinstances=40 --storagesystem=fusion

I propose the 10 runs corresponding to mosa and fusion be carried out by Hao
and Dongfang respectively. I can do the rest of the runs. I can work with Zhao
to build the synthetic workflow from his skeleton generation framework. Since
we will be working on identical cloud instances on same zones with servers etc
running within cloud, it nearly guarantees a uniform experimental environment
minimizing the chances of errors. We exchange log information after a first run
(pilot run) in each set and make sure we are in the same ballpark in terms of
general configuration etc.
